---
title: "Assignment B1"
output: github_document
---

## Required packages
```{r}
suppressPackageStartupMessages(library(datateachr))
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(testthat))
```

## Exercise 1&2: Make and document a Function
```{r}
#' @title Summarize numerical column statistical features by group
#' @details
#' Summarize statistical features of a numerical column in the data by group.
#' @param data A data frame contains data to be analyzed.
#' @param group the name of the variable that needs to group by.
#' @param column the name of the column to be summarized.
#' @return A tibble that contains summarized statistical features of given column by group.
summarize_by_group <- function (data, group, column) {
  
  # check if the data is data frame type
  stopifnot(is.data.frame(data))
  
  # convert input column into string name
  group_name <- rlang::as_label(rlang::enquo(group))
  column_name <- rlang::as_label(rlang::enquo(column))
  
  # check existence of given columns
  if (!(group_name %in% colnames(data)))
    stop("'", group_name, "' does not exist in the data")
  
  if (!(column_name %in% colnames(data)))
    stop("'", column_name, "' does not exist in the data")
  
  # get column data type
  column_type <- data %>% select({{column}}) %>% summarize_all(class)
  
  # check whether the column is numeric
  if (column_type[[1]] != "numeric")
    stop("'", column_name, "' data type must be numeric")
  
  # summarize statistical features of the column per group
  data %>% group_by({{group}}) %>% summarize(mean = mean({{column}}),
            range=max({{column}}) - min({{column}}), max=max({{column}}),
            min=min({{column}}), sd=sd({{column}}))
}

```


## Exercise 3: Include examples
Summarize column statistical features in `cancer_sample` dataset.

Summarize statistical features of radius_mean in cancer_sample
```{r}
summarize_by_group(cancer_sample, diagnosis, radius_mean)
```


Summarize statistical features of smoothness_mean in cancer_sample
```{r}
summarize_by_group(cancer_sample, diagnosis, smoothness_mean)
```


Test column existence validation. An error is expected since `smoothness_no` does not exist in `cancer_sample`.
```{r, error = TRUE}
summarize_by_group(cancer_sample, diagnosis, smoothness_no)
```


## Exercise 4: Test the Function
At least three non-redundant uses of an expect_() function for testing

```{r}
test_that("Input validation in summarize_by_group", {
    expect_error(summarize_by_group(cancer_sample, diagnosis, radius_me))
    expect_error(summarize_by_group(cancer_sample, NA, fractal_dimension_mean))
    expect_error(summarize_by_group(numeric(0), NA, compactness_mean))
})
```


```{r}
test_that("summarize_by_group outputs equal to known hash", {
    expect_known_hash(summarize_by_group(cancer_sample, diagnosis, radius_mean), "86b")
    expect_known_hash(summarize_by_group(cancer_sample, diagnosis, smoothness_mean), "f9b")
})
```

```{r}
test_that("summarize_by_group output data type is tibble", {
    expect_true(is_tibble(summarize_by_group(cancer_sample, diagnosis, texture_mean)))
    expect_false(any(is.na(summarize_by_group(cancer_sample, diagnosis, compactness_mean))))
})
```

